Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-01-05 WSSSPE3/report/WSSSPE3_review.tex
adding Mark Miller info

\author{Daniel S. Katz$^{(1)}$,
Kyle E.\ Niemeyer$^{(2)}$,
Sou-Cheng T. Choi$^{(3)}$,
James Hetherington$^{(4)}$,
Frank L\"{o}ffler$^{(5)}$,
Dan Gunter$^{(6)}$,
Ray Idaszak$^{(7)}$,
Steven R. Brandt$^{(5)}$,
Mark A. Miller$^{(7)}$,
Sandra Gesing$^{(9)}$,
Nick D. Jones$^{(10)}$,
Nic Weber$^{(11)}$,
Gabrielle Allen$^{(12)}$,
Colin C. Venters$^{(13)}$,
Ethan Davis$^{(14)}$,
Lorraine Hwang$^{(15)}$,
Ilian Todorov$^{(16)}$,
Abani Patra$^{(17)}$,
Miguel de Val-Borro$^{(18)}$,
}

%
\thanks{{}$^{(1)}$ Computation Institute, 
University of Chicago \& Argonne National Laboratory, Chicago, IL, USA; d.katz@ieee.org}
%
\thanks{{}$^{(2)}$ School of Mechanical, Industrial, and Manufacturing Engineering, 
Oregon State University, Corvallis, OR, USA; kyle.niemeyer@oregonstate.edu}
%
\thanks{{}$^{(3)}$ NORC at the University of Chicago and Illinois Institute of Technology, Chicago, IL, USA; sctchoi@uchicago.edu}
%
\thanks{{}$^{(4)}$ Research Software Development Group, University College London, UK; j.hetherington@ucl.ac.uk}
%
\thanks{{}$^{(5)}$ Center for Computation \& Technology, Louisiana State University, Baton Rouge, LA, USA; \{knarf,sbrandt\}@cct.lsu.edu}
%
\thanks{{}$^{(6)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(7)}$ RENCI, Chapel Hill, NC, USA; rayi@renci.org}
%
\thanks{{}$^{(8)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(9)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(10)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(11)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(12)}$ National Center for Supercomputing Applications, University of Illinois at Urbana-Champaign, Urbana, IL, USA, country; gdallen@illinois.edu}
%
\thanks{{}$^{(13)}$ School of Computing and Engineering, University of Huddersfield, Huddersfield, UK; C.Venters@hud.ac.uk}
%
\thanks{{}$^{(14)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(15)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(16)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(17)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(18)}$ Department of Astrophysical Sciences, 
Princeton University, Princeton, NJ, USA; mdevalbo@astro.princeton.edu}
%

>>>>

\author{Daniel S. Katz$^{(1)}$,
Kyle E.\ Niemeyer$^{(2)}$,
Sou-Cheng T. Choi$^{(3)}$,
James Hetherington$^{(4)}$,
Frank L\"{o}ffler$^{(5)}$,
Dan Gunter$^{(6)}$,
Ray Idaszak$^{(7)}$,
Steven R. Brandt$^{(5)}$,
Mark A. Miller$^{(8)}$,
Sandra Gesing$^{(9)}$,
Nick D. Jones$^{(10)}$,
Nic Weber$^{(11)}$,
Gabrielle Allen$^{(12)}$,
Colin C. Venters$^{(13)}$,
Ethan Davis$^{(14)}$,
Lorraine Hwang$^{(15)}$,
Ilian Todorov$^{(16)}$,
Abani Patra$^{(17)}$,
Miguel de Val-Borro$^{(18)}$,
}

%
\thanks{{}$^{(1)}$ Computation Institute, 
University of Chicago \& Argonne National Laboratory, Chicago, IL, USA; d.katz@ieee.org}
%
\thanks{{}$^{(2)}$ School of Mechanical, Industrial, and Manufacturing Engineering, 
Oregon State University, Corvallis, OR, USA; kyle.niemeyer@oregonstate.edu}
%
\thanks{{}$^{(3)}$ NORC at the University of Chicago and Illinois Institute of Technology, Chicago, IL, USA; sctchoi@uchicago.edu}
%
\thanks{{}$^{(4)}$ Research Software Development Group, University College London, UK; j.hetherington@ucl.ac.uk}
%
\thanks{{}$^{(5)}$ Center for Computation \& Technology, Louisiana State University, Baton Rouge, LA, USA; \{knarf,sbrandt\}@cct.lsu.edu}
%
\thanks{{}$^{(6)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(7)}$ RENCI, Chapel Hill, NC, USA; rayi@renci.org}
%
\thanks{{}$^{(8)}$ University of California, San Diego, CA, USA; mmiller@sdsc.edu}
%
\thanks{{}$^{(9)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(10)}$ New Zealand eScience Infrastructure (NeSI), University of Auckland, Auckland, NZ; nick.jones@nesi.org.nz}
%
\thanks{{}$^{(11)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(12)}$ National Center for Supercomputing Applications, University of Illinois at Urbana-Champaign, Urbana, IL, USA; gdallen@illinois.edu}
%
\thanks{{}$^{(13)}$ School of Computing and Engineering, University of Huddersfield, Huddersfield, UK; C.Venters@hud.ac.uk}
%
\thanks{{}$^{(14)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(15)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(16)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(17)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(18)}$ Department of Astrophysical Sciences, 
Princeton University, Princeton, NJ, USA; mdevalbo@astro.princeton.edu}
%

### 2016-01-05 WSSSPE3/report/wg_appendix_user_community.tex
moved all emails to footnotes for consistency

POC:
Dan Gunter <dkgunter@lbl.gov> and 
Ethan Davis <edavis@ucar.edu>

@@

No definite plans were agreed upon for future organizaton. The major ideas discussed
were coordinating with another group or adapting some existing text.

>>>>

POC:
Dan Gunter\footnote{email: \href{mailto:dkgunter@lbl.gov}{dkgunter@lbl.gov}} and 
Ethan Davis\footnote{email: \href{mailto:edavis@ucar.edu}{edavis@ucar.edu}}

@@

No definite plans were agreed upon for future organization. The major ideas discussed
were coordinating with another group or adapting some existing text.

### 2016-01-05 WSSSPE3/report/wg_main_publishing_SW.tex
Replied to Dan's note.

The plan is to create a web page describing executable papers, their value, and
a list of what publishers support them. \katznote{when?}

>>>>

The plan is to create and curate a web page describing executable papers, their value, and
a list of what publishers support them. We expect the page to be available in
early January of 2016 on the Software Sustainability Institute's website.

### 2016-01-05 WSSSPE3/report/wg_main_user_community.tex

This group doesn't have a landing page yet. Please send requests to join and contribute to both
Dan Gunter <dkgunter@lbl.gov> and Ethan Davis <edavis@ucar.edu>.

>>>>

This group doesn't have a landing page yet. Please send requests to join and contribute to both
Dan Gunter\footnote{email: \href{mailto:dkgunter@lbl.gov}{dkgunter@lbl.gov}} and Ethan Davis\footnote{email: \href{mailto:edavis@ucar.edu}{edavis@ucar.edu}}.
